Results

### 2021-07-23 Analysis/03_Summarise_results.Rmd
Added scaling + t.tests

```{r}
## Loading the functions
source("../Functions/summarise.results.R")
source("../Functions/plot.results.R")
```

@@

@@

```{r, fig.height = 4, fig.width = 12}
plot.results(all_results, metric = "alpha", level.names = removals, col = cols)
```

@@

```{r, fig.height = 4, fig.width = 12}
plot.results(all_results, metric = "dispersion", level.names = removals, col = cols)
```

@@

```{r, fig.height = 4, fig.width = 12}
plot.results(all_results, metric = "evenness", level.names = removals, col = cols, legend.pos = "bottomright")
```

@@

```{r, fig.height = 4, fig.width = 12}
plot.results(all_results, metric = "FD_Rao", level.names = removals, col = cols, legend.pos = "bottomright")
```

@@

```{r, fig.height = 4, fig.width = 12}
plot.results(all_results, metric = "FD_divergence", level.names = removals, col = cols, legend.pos = "bottomright")
```

@@

```{r, fig.height = 4, fig.width = 12}
plot.results(all_results, metric = "FD_evenness", level.names = removals, col = cols, legend.pos = "bottomright")
```

@@

```{r, fig.height = 4, fig.width = 12}
plot.results(all_results, metric = "melodic_Rao", level.names = removals, col = cols)
```

@@

```{r, fig.height = 4, fig.width = 12}
plot.results(all_results, metric = "melodic_mpd", level.names = removals, col = cols)
```

@@

```{r, fig.height = 4, fig.width = 12}
plot.results(all_results, metric = "convex.hull", level.names = removals, col = cols)
```

@@

```{r, fig.height = 4, fig.width = 12}
plot.results(all_results, metric = "hypervolume_richness", level.names = removals, col = cols)
```

@@

```{r, fig.height = 4, fig.width = 12}
plot.results(all_results, metric = "hypervolume_dispersion", level.names = removals, col = cols)
```

@@

```{r, fig.height = 4, fig.width = 12}
plot.results(all_results, metric = "hypervolume_regularity", level.names = removals, col = cols)
```

@@

```{r, fig.height = 4, fig.width = 12}
plot.results(all_results, metric = "TPD_Richness", level.names = removals, col = cols)
```

@@

```{r, fig.height = 4, fig.width = 12}
plot.results(all_results, metric = "TPD_Evenness", level.names = removals, col = cols)
```

@@

```{r, fig.height = 4, fig.width = 12}
plot.results(all_results, metric = "TPD_Divergence", level.names = removals, col = cols)
```

>>>>

```{r}
## Loading the functions
source("../Functions/extract.table.R")
source("../Functions/plot.metric.results.R")
source("../Functions/paired.tests.R")
```

@@

# TODOs:

  * [x]1. reworking the scaling
  * [ ]2. plotting the metrics per stressors (i.e. all metrics for each stressor).
    `TODO: re-work the plots (15 rows * 4 columns; each row is a metric and contains the lines for the 4 rarefactions; each column is a stressor)`
  * [ ]3. fitting a linear model per metric per stressor to rank models based on their r2
    > Pedro: Wonder if it makes sense to fit linear (or other) models to each trend (20, 40, 60, 80) and the higher the r2 the higher the clearer or more probable the detection of the trend?
  * [x]4. t-test (paired) of difference between each random score and the stressor
    `TODO 3+4: results table per metric`
  * [ ]5. run a psych-style pairwise comparison between each scaled metric
  * [ ]6. put the results in the context of the expectation table from the paper (Null vs process.docx)

## Scaling and centring the results

> TODO: we centre like this
> TODO: we scale like this

```{r}
## Extracting all the scaled results
scaled_results <- extract.table(all_results, scale.method = "between")
```

## Measuring the statistics for each metric

> TODO: we measure paired difference between random and stressor

```{r}
## Measuring the paired t-tests
metric_null_diff <- lapply(all_results, paired.tests)
```

@@

```{r, fig.height = 4, fig.width = 12}
plot.metric.results(all_results, metric = "alpha", scale.method = "within", level.names = removals, col = cols)
```

@@

```{r, fig.height = 4, fig.width = 12}
plot.metric.results(all_results, metric = "dispersion", scale.method = "within", level.names = removals, col = cols)
```

@@

```{r, fig.height = 4, fig.width = 12}
plot.metric.results(all_results, metric = "evenness", scale.method = "within", level.names = removals, col = cols, legend.pos = "bottomright")
```

@@

```{r, fig.height = 4, fig.width = 12}
plot.metric.results(all_results, metric = "FD_Rao", scale.method = "within", level.names = removals, col = cols, legend.pos = "bottomright")
```

@@

```{r, fig.height = 4, fig.width = 12}
plot.metric.results(all_results, metric = "FD_divergence", scale.method = "within", level.names = removals, col = cols, legend.pos = "bottomright")
```

@@

```{r, fig.height = 4, fig.width = 12}
plot.metric.results(all_results, metric = "FD_evenness", scale.method = "within", level.names = removals, col = cols, legend.pos = "bottomright")
```

@@

```{r, fig.height = 4, fig.width = 12}
plot.metric.results(all_results, metric = "melodic_Rao", scale.method = "within", level.names = removals, col = cols)
```

@@

```{r, fig.height = 4, fig.width = 12}
plot.metric.results(all_results, metric = "melodic_mpd", scale.method = "within", level.names = removals, col = cols)
```

@@

```{r, fig.height = 4, fig.width = 12}
plot.metric.results(all_results, metric = "convex.hull", scale.method = "within", level.names = removals, col = cols)
```

@@

```{r, fig.height = 4, fig.width = 12}
plot.metric.results(all_results, metric = "hypervolume_richness", scale.method = "within", level.names = removals, col = cols)
```

@@

```{r, fig.height = 4, fig.width = 12}
plot.metric.results(all_results, metric = "hypervolume_dispersion", scale.method = "within", level.names = removals, col = cols)
```

@@

```{r, fig.height = 4, fig.width = 12}
plot.metric.results(all_results, metric = "hypervolume_regularity", scale.method = "within", level.names = removals, col = cols)
```

@@

```{r, fig.height = 4, fig.width = 12}
plot.metric.results(all_results, metric = "TPD_Richness", scale.method = "within", level.names = removals, col = cols)
```

@@

```{r, fig.height = 4, fig.width = 12}
plot.metric.results(all_results, metric = "TPD_Evenness", scale.method = "within", level.names = removals, col = cols)
```

@@

```{r, fig.height = 4, fig.width = 12}
plot.metric.results(all_results, metric = "TPD_Divergence", scale.method = "within", level.names = removals, col = cols)
```
